The Splashback Radius of Planck-SZ clusters

### 2019-03-13 Paper_v2/RSP_paper_new.tex
changed bibliography

This paper is organized as follows. We introduce the observational
data sets we use in Section~\ref{sec:data}, namely the cluster and the
galaxy catalogs. We describe the methods and analysis procedures we
use in Section~\ref{sec:estimators}. We present and discuss our
results in Section~\ref{sec:Results}. Finally, we summarize our
findings in Section~\ref{sec:Conclusions} and discuss possible future
directions. Throughout the paper, we use a flat $\Lambda$CDM cosmology
with $\Omega_{\rm m}=0.27$ and a dimensionless Hubble parameter of $h=0.7$
to convert redshifts and angles into
cosmological distances. Also, we denote three-dimensional distances by
$r$ and projected distances by $R$.

@@

While this work was in preparation, we became aware of a related study
namely, \citet{shin2018des}. Our results are complementary to theirs given
the different data samples and cluster catalogs.

@@

Based on observations obtained with Planck
(http://www.esa.int/Planck), an ESA science mission with instruments
and contributions directly funded by ESA Member States, NASA, and
Canada.  Some of the results in this paper have been derived using
the HEALPix (K.M. Górski et al., 2005, ApJ, 622, p759) package

>>>>

This paper is organized as follows. We introduce the observational
data sets we use in Section~\ref{sec:data}, namely the cluster and the
galaxy catalogs. We describe the methods and analysis procedures we
use in Section~\ref{sec:estimators}. We present and discuss our
results in Section~\ref{sec:Results}. Finally, we summarize our
findings in Section~\ref{sec:Conclusions} and discuss possible future
directions. Throughout the paper, we use a flat $\Lambda$CDM cosmology
with $\Omega_{\rm m}=0.27$ and a dimensionless Hubble parameter of $h=0.7$
to convert redshifts and angles into
cosmological distances. Also, we denote three-dimensional distances by
$r$ and projected distances by $R$. All distance measurements in this 
paper are given in comoving units.

@@

While this work was in preparation, we became aware of a related study
by \citet{shin2018des}. Our results are complementary to theirs given
the different data samples and cluster catalogs.

@@

Based on observations obtained with Planck
(http://www.esa.int/Planck), an ESA science mission with instruments
and contributions directly funded by ESA Member States, NASA, and
Canada.  Some of the results in this paper have been derived using
the HEALPix package \citep{gorski2005}
